The Neuro Bureau ADHD-200 Preprocessed Repository

### 2015-12-25 Bellec_ADHD200_2016.tex

\begin{table}[htbp]
\label{tab_parcellations}
\caption{{\bf Summary of the characteristics of all brain parcellations used in the ADHD-200 Preprocessed release.} Sizes for the parcels are reported in mm$^3$.}
\begin{tabular}{llrrrrr}
Name & Type & \# parcels & mean size & std size & min size & max size \\
\hline
AAL	    & anatomical &  116 &  16726 & 11896 &  768 & 55552\\
EZ	    & anatomical &  116 &  15880 & 11059 & 1344 & 52608\\
HO	    & anatomical &  111 &  14540 & 15342 &   64 & 99200\\
TT	    & anatomical & 	 97 &  17106 & 16164 &   64 & 70400\\
CC200   & functional &  190 &  11351 &  2001 & 2880 & 17856\\
CC400   & functional &  351 &   6144 &  1207 &   64 & 10048\\
ROI1000 & functional &  954 &   1404 &   366 &   27 & 2781\\
ROI3000	& functional & 2843	&    471 &   109 &   27 & 1026\\
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\label{tab_parcellations}
\caption{{\bf Summary of the characteristics of all brain parcellations used in the ADHD-200 Preprocessed release.} Sizes for the parcels are reported in mm$^3$.}
\begin{tabular}{llrrrrr}
Name & Type & \# parcels & mean size & std size & min size & max size \\
\hline
AAL	    & structural &  116 &  16726 & 11896 &  768 & 55552\\
EZ	    & structural &  116 &  15880 & 11059 & 1344 & 52608\\
HO	    & structural &  111 &  14540 & 15342 &   64 & 99200\\
TT	    & structural & 	 97 &  17106 & 16164 &   64 & 70400\\
CC200   & functional &  190 &  11351 &  2001 & 2880 & 17856\\
CC400   & functional &  351 &   6144 &  1207 &   64 & 10048\\
ROI1000 & functional &  954 &   1404 &   366 &   27 & 2781\\
ROI3000	& functional & 2843	&    471 &   109 &   27 & 1026\\
\end{tabular}
\end{table}
